Evolution of Processes in Delivering Reliable Software in the European Scientific Arena

### 2018-06-15 paper-ieee-trans.tex
fix
fix criteria (plural)

The SQA criteria are a set of conventions and recommendations that pave the way for
the adequate development, timely delivery and reliable operation of the produced software components.
It emphasizes the quality requirements and best practices to be applied at the
development phase, such as style and testing compliance or human code reviews, to protect the
production source code versions. Furthermore, the criteria promote the adoption of the software
by providing minimum requirements of documentation content and stressing the usage of automated
solutions for software deployment. The SQA criteria is continuously evolving \cite{sqa-baseline}, aiming at serving
as a reference for future software development projects within the European research ecosystem.

@@

Lessons learned showed that sustainability must be a key pursuit. The achievements, in terms of
processes, knowledge, software and infrastructures, shall be profited from former successful 
completed projects. In this regard, the more recent project described in this paper, {\sl INDIGO-DataCloud},
may have set the path for future reference in the European software development research ecosystem.
The SQA criteria, describing the quality requirements that might be considered during the entire
software lifecycle, has been published as open access and it is periodically reviewed to incorporate
new recommendations and best practices. Successful software products created during the lifetime of the 
project are maintained leveraging the same source code repositories and CI infrastructure. Seamless 
knowledge transfer among software development initiatives is key for the good progress of delivering
reliable software.

>>>>

The SQA criteria are a set of conventions and recommendations that pave the way for
the adequate development, timely delivery and reliable operation of the produced software components.
It emphasizes the quality requirements and best practices to be applied at the
development phase, such as style and testing compliance or human code reviews, to protect the
production source code versions. Furthermore, the criteria promote the adoption of the software
by providing minimum requirements of documentation content and stressing the usage of automated
solutions for software deployment. The SQA criteria are continuously evolving \cite{sqa-baseline}, aiming at serving
as a reference for future software development projects within the European research ecosystem.

@@

Lessons learned show that sustainability is a key pursuit. The achievements, in terms of
processes, knowledge, software and infrastructures, shall be profited from former successful 
completed projects. In this regard, the more recent project described in this paper, {\sl INDIGO-DataCloud},
may have set the path for future reference in the European software development research ecosystem.
The SQA criteria, describing the quality requirements that might be considered during the entire
software lifecycle, have been published as open access and it is periodically reviewed to incorporate
new recommendations and best practices. Successful software products created during the lifetime of the 
project are maintained leveraging the same source code repositories and CI infrastructure. Seamless 
knowledge transfer among software development initiatives is key for the good progress of delivering
reliable software.
